Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Fix wrapping
Fix reference

Previous research on social movements supports the idea that participants are
likely to join movements when they know and have a personal connection to
someone else already involved [@mcadam1986recruitment]. The type of collective
contentious behavior that manifests in society is a function of the available
political opportunity structures. The political opportunity structure are
“comprised *(sic)* of specific configuration of resources, institutional
arrangements and historical precedents for social mobilization, which facilitate
the development of protest movements in some instances and constrain them in
others” [@Kitschelt_1986]. What emerges as strategies and tactics in contentious
politics are, in essence, a function of what the system makes possible. This
includes the number of people and their disposition (i.e. nonviolent or
violent), as well as their internal structure. The more cohesive a group is, the
greater threat they pose to the establishment.

>>>>

Previous research on social movements supports the idea that participants are
likely to join movements when they know and have a personal connection to
someone else already involved [@mcadam1986recruitment]. The type of collective
contentious behavior that manifests in society is a function of the available
political opportunity structures. The political opportunity structure are
“comprised *(sic)* of specific configuration of resources, institutional
arrangements and historical precedents for social mobilization, which facilitate
the development of protest movements in some instances and constrain them in
others” [@kitschelt1986political]. What emerges as strategies and tactics in
contentious politics are, in essence, a function of what the system makes
possible. This includes the number of people and their disposition (i.e.
nonviolent or violent), as well as their internal structure. The more cohesive a
group is, the greater threat they pose to the establishment.
